MSAD_PCA_Walkthrough

### 2017-03-27 README.Rmd
Update README.Rmd
Added a random draw from mspProcessData(), and updated the god-awful lag bit.

## Overview
We create this package, `mvMonitor`, from the foundation laid by Kazor et al (2016). The `mvMonitor` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.

@@

## Examples
These are the examples shown in the help files for hte mspTrain(), mspMonitor(), and mspWarning() functions.
```{r mspExamples}
data("normal_switch_xts")
# The state values are recorded in the first column.
n <- nrow(normal_switch_xts)
nTrainObs <- floor(0.4 * n)

@@

# While training, we included 1 lag (the default), so we will also lag the
# observations we will test.
testObs <- normal_switch_xts[(n - 6):n, -1]
testObs <- stats::lag(zoo::zoo(testObs), 0:-1)
testObs <- xts::xts(testObs[-1,])
testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
testObs

>>>>

## Overview
We create this package, `mvMonitoring`, from the foundation laid by Kazor et al (2016). The `mvMonitor` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.

@@

## Examples
These are the examples shown in the help files for the mspTrain(), mspMonitor(), and mspWarning() functions.
```{r mspExamples}
normal_switch_xts <- mspProcessData(faults = "NOC", faultStartIndex = 8500)
# The state values are recorded in the first column.
n <- nrow(normal_switch_xts)
nTrainObs <- floor(0.4 * n)

@@

# While training, we included 1 lag (the default), so we will also lag the
# observations we will test.
testObs <- normal_switch_xts[(n - 6):n, -1]
testObs <- xts:::lag.xts(testObs, 0:1)
testObs <- testObs[-1,]
testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
testObs
